### 2015-05-14 paper.tex
citations
some cleanup

Here we review work done on approximations for clustering algorithms, focusing on the work of \cite{firstpaper} and \cite{secondpaper}. The essential goal is that for various data points about objects of interest, we can group those data points by which object they belong to. For example we may have a collection of face images, collect a relatively low dimensional datapoint (feature vector) for each image, and then cluster this data to try to determine whether images came from the same people (each cluster corresponding to a distinct person). However the problem of clustering points given a distance metric is in general NP-hard. Additionally, analysis of clustering alone does not take into account the relationship between the clusters and the underlying object they belong to. For example, even if the images were clustered optimally, according to some objective function, that clustering may not correctly group the images by which person's face is in the image if the choice of objective function were not a perfect match for the problem. The work here will focus on algorithms for approximating correct clustering.

@@

\subsection{($c, \delta$)-property}
Thus far we have only addressed clustering based on the data points, but not the underlying objectives interest. TODO: Andy note: that's not true, we just talked about the objective above...

The \textbf{objective} function $\Phi(C)$ is the cost of a clustering based only on the distance between points. However the optimal \textbf{target} clustering is that which partitions the points best based on the underlying objects the data points are drawn from. In the ideal problem statement the optimal objective clustering $C^*$ and the optimal target clustering $C^T$ are the same. However in practice this is not usually the case. In order to be able to perform analysis on the quality of a clustering \cite{firstpaper} define the $(c, \delta)$-property.  If a clustering satisfies the $(c, \delta)$-property, then for all clusterings where $\Phi(C) \leq c*\text{OPT}_\Phi$, $C$ is also $\delta$-close to $C^T$. By analyzing problem instances where this holds true for some values of $c$ and $\delta$, we can generate approximate clustering schema to achieve approximation solutions to discovering the target clustering.

@@

The goal of this work is to develop a polynomial runtime clustering algorithm with minimal constraints on the values of $c$ and $\delta$ as described above. It is known that a better than $1 + \frac{2}{\delta}$ approximation for k-medians is NP-hard \cite{thethingthepapercitesJMS02}. In this review we will show explore the following results:

@@

@@

This paper looks at a few statistics about how points are distributed and how it relates to optimal clusterings.  In particular, it studies notions of "stability," which describes bounds on how much adding or removing clusters from a clustering solution changes the objective function's value, and separability, which describes how far away clusters of points are from one another.  By characterizing point sets in terms of these statistics, the authors derive an algorithm for efficiently clustering the points and derive guarantees on the cluster quality, as well as prove its correctness.

\subsection{Definitions}
The paper begins by describing a few statistics on the point distributions which are necessary for the subsequent analysis.  Let $OPT_i$ be the contribution to the objective function of the optimal clustering by cluster $i$, and let $OPT^{i \rightarrow j}$ denote the the cost when cluster $i$ is removed from the $OPT$ solution (which, for simplicity's sake, we will assume to be unique) and its points are then given to cluster $j$.  Intuitively, $OPT^{i \rightarrow j}$ corresponds to a (bad) solution of a $k-1$ clustering, and $OPT(k)^{i \rightarrow j} \geq OPT(k-1)$, where $OPT(f)$ is the optimal solution of the $f$ cluster problem.  Let a clustering be $(1 + \alpha)$ weak-deletion stable if, $\forall i \neq j, OPT^{i \rightarrow j} > (1 + \alpha)OPT$ - in other words, removing any cluster and remapping those points to another single cluster severely contributes to the objective function, suggesting that that each cluster is significant to the solution. Intuitively if this is not the case, then one could reasonably use the ($k-1$) solution in place of the $k$ solution.

@@

Let's begin by partitioning our set of clusters into two types.  There are  "cheap" clusters and "expensive" clusters, with the idea being that the expensive clusters contribute a larger amount to the cost than the cheaper clusters; in other words, we have mostly densely packed groups of points, and a few not-so densely packed groups.  The key idea is to assume (and later we prove) that the number of expensive clusters is \emph{bounded}.  We then have a method for clustering the cheap point sets, assuming we can partition cheap and expensive points: guess the number of points in the cheap clusters, derive a relationship from the number of points to the radius $r$ of that point set, and then draw balls of radius $r$ around the points in each of those sets.  In order to cluster the expensive points, we then use brute force to guess each of the remaining cluster centers, and since the number of remaining clusters is bounded and small, this brute force operation should not contribute significantly to the runtime.  This all hinges on being able to partition the points into cheap and expensive sets, which arises naturally out of the procedure.  In practice, the algorithm attempts to create a list of possible subsets of points (which could overlap in membership), and iteratively refine that list to create our $k$ clusters.

@@

>>>>

Here we review work done on approximations for clustering algorithms, focusing on the work of \cite{firstpaper} and \cite{secondpaper}. The essential goal is that for various data points about sets of interest, we wish to group those data points by which set they belong to. For example we may have a collection of face images, generate a relatively low dimensional datapoint (feature vector) for each image, and then cluster this data to try to determine whether images came from the same people (each cluster corresponding to a distinct person). However the problem of clustering points given a distance metric is in general NP-hard. Additionally, analysis of clustering alone does not take into account the relationship between the clusters and the underlying sets they belong to. For example, even if the images were clustered optimally, according to some objective function of distance between datapoints, that clustering may not correctly group the images by which person's face is in the image. The work here will focus on algorithms for approximating correct clustering based on the underlying sets.

@@

\subsection{($c, \delta$)-property}
Thus far we have only addressed clustering based on the data points, but not the underlying sets of interest.

The \textbf{objective} function $\Phi(C)$ is the cost of a clustering based only on the distance between points. However the optimal \textbf{target} clustering is that which partitions the points best based on the underlying sets the data points are drawn from. In the ideal problem statement the optimal objective clustering $C^*$ and the optimal target clustering $C^T$ are the same. However in practice this is not usually the case. In order to be able to perform analysis on the quality of a clustering \cite{firstpaper} define the $(c, \delta)$-property.  If a clustering satisfies the $(c, \delta)$-property, then for all clusterings where $\Phi(C) \leq c*\text{OPT}_\Phi$, $C$ is also $\delta$-close to $C^T$. By analyzing problem instances where this holds true for some values of $c$ and $\delta$, we can generate approximate clustering schema to achieve approximation solutions to discovering the target clustering.

@@

The goal of this work is to develop a polynomial runtime clustering algorithm with minimal constraints on the values of $c$ and $\delta$ as described above. It is known that a better than $1 + \frac{2}{\delta}$ approximation for k-medians is NP-hard \cite{JMS02}. In this review we will show explore the following results:

@@

\item Assume we have a problem with a $(1+\alpha, \delta)$-property, with no restriction on cluster size. There exists n $O(\delta/\alpha)$-close to the target and an algorithm for finding this clustering.
\end{itemize}

@@

This paper looks at a few statistics about how points are distributed and how it relates to optimal clusterings.  In particular, it studies notions of stability, which describes bounds on how much adding or removing clusters from a clustering solution changes the objective function's value, as well as the notion of separability, which describes how far away clusters of points are from one another.  By characterizing point sets in terms of these statistics, the authors derive an algorithm for efficiently clustering the points and derive guarantees on the cluster quality.
\subsection{Definitions}
The paper begins by describing a few statistics on the point distributions which are necessary for the subsequent analysis.  Let $OPT_i$ be the contribution to the objective function of the optimal clustering by cluster $i$, and let $OPT^{i \rightarrow j}$ denote the the cost when cluster $i$ is removed from the $OPT$ solution (which, for simplicity's sake, we will assume to be unique) and its points are then given to cluster $j$.  Intuitively, $OPT^{i \rightarrow j}$ corresponds to a (bad) solution of a $k-1$ clustering, and $OPT(k)^{i \rightarrow j} \geq OPT(k-1)$, where $OPT(f)$ is the optimal solution of the $f$-cluster problem.  Let a clustering be $(1 + \alpha)$ weak-deletion stable if, $\forall i \neq j, OPT^{i \rightarrow j} > (1 + \alpha)OPT$ - in other words, removing any cluster and remapping those points to another single cluster severely contributes to the objective function, suggesting that that each cluster is significant to the solution. Intuitively if this is not the case, then one could reasonably use the ($k-1$) solution in place of the $k$ solution.

@@

To complete the notion of a cheap cluster, we define an expensive cluster to be one with $\text{OPT}_i > \frac{\beta\epsilon\text{OPT}}{32}$. The key idea is to assume (and later we prove) that the number of expensive clusters is \emph{bounded}.  We then have a method for clustering the cheap point sets, assuming we can partition cheap and expensive points: guess the number of points in the cheap clusters, derive a relationship from the number of points to the radius $r$ of that point set, and then draw balls of radius $r$ around the points in each of those sets.  In order to cluster the expensive points, we then use brute force to guess each of the remaining cluster centers, and since the number of remaining clusters is bounded and small, this brute force operation should not contribute significantly to the runtime.  This all hinges on being able to partition the points into cheap and expensive sets, which arises naturally out of the procedure.  In practice, the algorithm attempts to create a list of possible subsets of points (which could overlap in membership), and iteratively refine that list to create our $k$ clusters.

@@

\end{itemize}
\bibliography{biblio}{}
\bibliographystyle{plain}
